### 2022-05-06 paper/ase22/experiment.tex
edit exp & table

\section{Experimental Setup}
\label{sec:experiment}
%

% \InputWithSpace{tables/retrain-debug-table}

In this section, we present the setup of the experiments to evaluate
the effectiveness of \tool{}. We address the following research
questions (RQs):

@@

\begin{enumerate}[label=\textbf{RQ\arabic*}]
\item \label{rq:one}: Can \tool generate consistent test sentence and
  its oracle?
\item \label{rq:two}: Is \tool generated testcases relevant to be used
  for their \lc evaluation?
\item \label{rq:three}: Can \tool generate more diverse test cases
  than \Cklst?
\item \label{rq:four}: Can \tool be useful to find root causes of bugs
  in the \sa models?
%% \item \label{rq:three}: How effective is our new test case generation
%%   using \cfg expansion? % ablation study
\end{enumerate}

@@

@@

In the manual study, we randomly sample three sets of pairs of seed
sentences and corresponding \lc from seed test cases. For each set, we
also select expanded sentences that \tool generated from the formerly
sampled seed sentences. In this experiment, each set has 100 sentences
(50 from seed sentences and 50 from expanded sentences) and 300
sentences, in total, are used for the manual study. For each sampled
set, two subjects are provided with the same set of sampled
sentences. The subjects are asked for scoring the two following:
\textbf{1. relevancy score between sentence and its associated \lc}:
this score measures the amount of appropriateness of the use of
sentence for evaluating the model on its \lc.  The scores are discrete
ranging from 1 to 5, and each represents ``strongly not relevant'' to
``strongly relevant'' respectively. \textbf{2. sentiment score of
  sentence}: this score measures the level of sentence sentiment. It
is also discrete, and it ranges from 1 to 5 representing ``strongly
negative'' to ``strongly positive'' respectively. In this work, we
collect manual study scores from 6 subjects in total. From the
collected scores, we measure the following metrics:

@@

The equation~\ref{metric:srel} represent the number of test cases that
their labels assigned from are different between \tool and
human. Higher number of this metric indicates worse correlation of
test oracle that \tool generated with human. In addition, the
equation~\ref{metric:lcrel} represents the average score of the
relevancy score between sentence and its associated \lc. higer average
score means that higher human-level agreement of the use of sentence
for its \lc, resulting in higher suitability of the use of the
testcases for evaluating model on the \lc. Given the metrics, we
answer RQ1 and RQ2 by the metrics from the equation~\ref{metric:srel}
and equation~\ref{metric:lcrel} respectively, thereby, show its ability
of \tool to understand human intelligence.

\paragraph{RQ3.}
Recall that a key limitation of \Cklst is that its template-based
approach that relies on significant manual efforts may not generate
test cases that comprehensively cover the sentences in a linguistic
capability. \tool, instead, automatically generates test cases based
on a search dataset and the syntax in a large reference corpus. We
expect \tool can generate a more diverse test suite than \Cklst. To
measure diversity, we follow the approach presented by Ma et
al. \cite{ma2018deepgauge}, where the authors measure the coverage of
NLP model intermediate states as corner-case neurons.  \sw{Why is this
  a good metric for diversity?}  Specifically, we use the \sw{are
  these metrics we define or are they from ma2018deepgauge?} two
coverage metrics in existing work \cite{ma2018deepgauge},
\textit{boundary coverage} (BoundCov) and \textit{strong activation
  coverage} (SActCov), as our metrics to evaluate the test suite
diversity.

\begin{equation}
\begin{split}
    \text{UpperCornerNeuron}(\mathcal{X}) = \{n \in N | \exists x \in \mathcal{X}: f_n(x) \in (high_n, +\infty)\}; \\
    \text{LowerCornerNeuron}(\mathcal{X}) = \{n \in N | \exists x \in \mathcal{X}: f_n(x) \in (-\infty, low_n)\}; \\
\end{split}
    \label{eq:corner}
\end{equation}

@@

\begin{equation}
\begin{split}
     & BoundCov(\mathcal{X}) = \frac{|UpperCornerNeuron(\mathcal{X})| + |LowerCornerNeuron| }{2 \times |N|} \\ 
     & SActCov(\mathcal{X}) = \frac{|UpperCornerNeuron(\mathcal{X})|} {|N|} \\ 
\end{split}
    \label{eq:coverage}
\end{equation}

@@

To answer {\bf RQ3}, for each NLP model under test, we first feed its training dataset to compute each neuron's lower and upper bounds. After that, we randomly select 100 \sw{Why 100, not all?} test cases from \tool and \Cklst as the test suite and compute the corresponding coverage metrics. 
\cm{we repeat this process and record both the average and variance value of each coverage}
% For each subject, we randomly select 100 seed samples from the test dataset as seed inputs. We then feed the same seed inputs into \tool and \texttt{ILFO} to generate test samples. 
% Finally, we feed the generated test samples to AdNNs and measure block coverage.
% We repeat this process 10 times and record the average coverage and the variance.
% The results are shown in \tabref{tab:coverage} last two columns.

@@

\paragraph{RQ4.} To demonstrate that \tool can help developers to understand the bugs in the sentiment analysis modes, we conduct experiments to visualize

\sw{@Simin: add the setup of the bug explanation case study here.}
%In addition to the detection of bugs \sw{have we defined ``bug" in this context?} in the model,
%explanation of the bugs is also important for debugging and
%repairing the model. Therefore, we answer {\bf RQ3} by analyzing the \sa model based on \tool test cases to find the root causes of the bugs.
%
%Specifically, we adapt \Denas{} for this experiment. \sw{Say more what DENAS does.} Rules generated from
%\Denas{} are interpretable functions mapping certain features of the
%input to the expected output of a deep \nn system, and the generated
%rules are considered as the behaviors of the deep \nn system. To
%analyze the bug of a \sa model, we generates rules over the test
%inputs using \Denas{} and identifies faulty rules for the failed test
%inputs.
%\sw{Previous sounds vague. Any specific adaptation of DENAS we did?}
%We manually identify the root of the faulty rules and find the
%root causes of bug in the end.

>>>>

\section{Experimental Setup}
\label{sec:experiment}
%
In this section, we present the setup of the experiments to evaluate
the effectiveness of \tool{}. We address the following research
questions (RQs):

@@

\begin{enumerate}[label=\textbf{RQ\arabic*}]
\item \label{rq:one}: Can \tool generate consistent test sentence and
  its oracle?
\item \label{rq:two}: Are \tool generated test cases relevant to be used
  for their \lc evaluation?
\item \label{rq:three}: Can \tool generate more diverse test cases
  than \Cklst?
\item \label{rq:four}: Can \tool be useful to find root causes of bugs
  in the \sa models?
%% \item \label{rq:three}: How effective is our new test case generation
%%   using \cfg expansion? % ablation study
\end{enumerate}

@@

\subsection{Experimental Subjects}

\paragraph{\textbf{NLP Models \& Dataset.}}
We evaluate our approach on three leaerning-based \sa models
implemented in Transformer library from the Hugging Face centralized
Model Hub.\footnote{https://huggingface.co/models}: \texttt{\Bert}
(\bertsamodel), \texttt{\Roberta} (\robertasamodel), and
\texttt{\Dbert} (\disbertsamodel). They are pre-trained on English
language using a masked language modeling (MLM) objective, and
fine-tuned on \sa task. In this experiment, we use \Sstt dataset for
searching seeds and expanding the seeds in \tool.
%% \TODO{introduce details about each model}

\paragraph{\textbf{Comparison Baselines.}}
We compare our approach with
\Cklst\footnote{https://github.com/marcotcr/checklist}, which is a
manual template-based approach to generate test cases. In this
experiment, we used the \Cklst released \sa test cases which are
generated from its publicly available jupyter notebook implementation.
%% \TODO{introduce details about CHECKLIST}

\subsection{Experimental Process}

@@

In the manual study, we randomly sample three sets of pairs of seed
sentences and corresponding \lc from seed test cases. For each set, we
also select expanded sentences that \tool generated from the formerly
sampled seed sentences. In this experiment, each set has 100 sentences
(50 from seed sentences and 50 from expanded sentences) and 200
sentences, in total, are used for the manual study. For each sampled
set, two subjects are provided with the same set of sampled
sentences. The subjects are asked for scoring the two following:
\textbf{1. relevancy score between sentence and its associated \lc}:
this score measures the amount of appropriateness of the use of
sentence for evaluating the model on its \lc.  The scores are discrete
ranging from 1 to 5, and each represents ``strongly not relevant'' to
``strongly relevant'' respectively. \textbf{2. sentiment score of
  sentence}: this score measures the level of sentence sentiment. It
is also discrete, and it ranges from 1 to 5 representing ``strongly
negative'' to ``strongly positive'' respectively. In this work, we
collect manual study scores from 3 subjects in total. In case of
different scores with a same sentence from different subjects, we used
their average score as a score of the sentence.
%% \sw{6 or 3 participants? What happened if participants scored differently?}
From the collected scores, we measure the following metrics:

@@

The equation~\ref{metric:srel} represent the number of test cases that
their labels assigned from are different between \tool and
human. Higher number of this metric indicates worse correlation of
test oracle that \tool generated with human. In addition, the
equation~\ref{metric:lcrel} represents the average score of the
relevancy score between sentence and its associated \lc. Higer average
score means that higher human-level agreement of the use of sentence
for its \lc, resulting in higher suitability of the use of the
testcases for evaluating model on the \lc. Given the metrics, we
answer RQ1 and RQ2 by the metrics from the equation~\ref{metric:srel}
and equation~\ref{metric:lcrel} respectively, thereby, show its
ability of \tool to understand human intelligence.

\paragraph{RQ3.}
Recall that a key limitation of \Cklst is that its template-based
approach that relies on significant manual efforts may not generate
test cases that comprehensively cover the sentences in a linguistic
capability. \tool, instead, automatically generates test cases based
on a search dataset and the syntax in a large reference corpus. We
expect \tool can generate a more diverse test suite than \Cklst. To
measure diversity, we follow the approach presented by Ma et
al. \cite{ma2018deepgauge}, where the authors measure the coverage of
NLP model intermediate states as corner-case neurons.  Because the
matrix computation of intermediate states impacts NLP model
decision-making, a test suite that covers a greater number of
intermediate states can represent more NLP model decision-making,
making it more diverse.  Specifically, we used two coverage metrics in
existing work \cite{ma2018deepgauge}, \textit{boundary coverage}
(BoundCov) and \textit{strong activation coverage} (SActCov), as our
metrics to evaluate the test suite diversity.  \TODO{It is worth
  noting that a test sample with a statistical distribution similar to
  the training data would rarely be found in the corner case
  region. As a result, covering a larger corner case region means that
  the test suite is more likely to be buggy.}

\begin{equation}
\begin{split}
    \text{UpperCorner}(\mathcal{X}) = \{n \in N | \exists x \in \mathcal{X}: f_n(x) \in (high_n, +\infty)\}; \\
    \text{LowerCorner}(\mathcal{X}) = \{n \in N | \exists x \in \mathcal{X}: f_n(x) \in (-\infty, low_n)\}; \\
\end{split}
    \label{eq:corner}
\end{equation}

@@

\begin{equation}
\begin{split}
     & BoundCov(\mathcal{X}) = \frac{|UpperCorner(\mathcal{X})| + |LowerCorner(\mathcal{X})| }{2 \times |N|} \\ 
     &\quad  \qquad \qquad  SActCov(\mathcal{X}) = \frac{|UpperCorner(\mathcal{X})|} {|N|} \\ 
\end{split}
    \label{eq:coverage}
\end{equation}

@@

To answer {\bf RQ3}, for each NLP model under test, we first feed its training dataset to compute each neuron's lower and upper bounds. After that, we select the same number of test cases from \tool and \Cklst as the test suite and compute the corresponding coverage metrics.

% For each subject, we randomly select 100 seed samples from the test dataset as seed inputs. We then feed the same seed inputs into \tool and \texttt{ILFO} to generate test samples. 
% Finally, we feed the generated test samples to AdNNs and measure block coverage.
% We repeat this process 10 times and record the average coverage and the variance.
% The results are shown in \tabref{tab:coverage} last two columns.

@@

\paragraph{RQ4.}

To answer RQ4, we conduct experiments to demonstrate that \tool can help developers understand the bugs in the NLP models.
Recall that \tool generates test cases by mutating seed sentences (\eg by expanding one token in the seed input). Still, it is unclear why mutating one token will cause the model to produce misclassified results.
We seek to help developers to understand why such mutation will result in the misclassification. 
Existing work \cite{simin2020denas, lemna, lime} has demonstrated that the ML model prediction is dominated by a minimal set of input features (\ie tokens in input sentences). Motivated by such intuition, we seek to identify a minimal set of input tokens that dominate the model prediction.

Formally, given a input sentence $x = [tk_1, tk_2, \cdots, tk_n]$, and the NLP model under test $f(\cdot)$, our goal is to find a masking template $T = [t_1, t_2, \cdots, t_n]$, where $t_i$ is 0 or 1, representing masking the $i^{th}$ token in $x$ or not.
The template $T$ can mask some tokens in $x$ with attribute tokens, and the masked input has a high probability of retaining the original prediction $x$, denoted as

\begin{equation}
    P(f(T(x)) = f(x)) \ge P_{thresh}
    \label{eq:prob}
\end{equation}

To create such a template $T$, we first compute the contribution score of each input token using an existing explainable ML technique \cite{}. Following that, we begin with the full mask template (\ie, all tokens are masked); such full mask template definitely does not satisfy Eq. \ref{eq:prob}.
We then iteratively shift one position from mask to non-mask based on the order of each token's contribution score, until the template $T$ satisfies Eq. \ref{eq:prob}
Because we iterate the size of our mask, the generated template $T$ will keep the minimum number of tokens in $x$. Moreover, since the input $x$ is an incorrect prediction, the generated template $T$ is likely to produce misclassification (i.e., the probability to be misclassified is larger than $P_{thresh}$).

% In particular, we apply the explainable ML techniques to visualize the contribution of each input token to the model predictions.
%

% \sw{@Simin: add the setup of the bug explanation case study here.}
%In addition to the detection of bugs \sw{have we defined ``bug" in this context?} in the model,
%explanation of the bugs is also important for debugging and
%repairing the model. Therefore, we answer {\bf RQ3} by analyzing the \sa model based on \tool test cases to find the root causes of the bugs.
%
%Specifically, we adapt \Denas{} for this experiment. \sw{Say more what DENAS does.} Rules generated from
%\Denas{} are interpretable functions mapping certain features of the
%input to the expected output of a deep \nn system, and the generated
%rules are considered as the behaviors of the deep \nn system. To
%analyze the bug of a \sa model, we generates rules over the test
%inputs using \Denas{} and identifies faulty rules for the failed test
%inputs.
%\sw{Previous sounds vague. Any specific adaptation of DENAS we did?}
%We manually identify the root of the faulty rules and find the
%root causes of bug in the end.
